---
title: "R Notebook"
output: html_notebook
---


# 0.0 Imports

```{r}
renv::restore()
```


```{r}
library(tidyverse)
library(nycflights13)
```


# 1.0 Tidy Data

Exercises

1) table 1: represents cases and country population per country and year
   table 2: each observation represents a country, year and specific indicator (cases or population). The three first columns are categorical about the count color
   table 3: each observation represents a rate of TB case per year and country.


2) table 1: I would use mutate
   table 2: I would pivot type and count, them merge
   table 3: I would split the rate column into two strings, using the / as delimitator, then I would name the columns

# 2.0 Lengthening Data

```{r}
billboard_longer <- billboard |> 
  pivot_longer(
    cols = starts_with("wk"),
    names_to = "week",
    values_to = "rank",
    values_drop_na = TRUE
  ) |> 
  mutate(
    week = parse_number(week)
  )
billboard_longer
```


```{r}
billboard_longer |> 
  ggplot(aes(x = week, y = rank)) +
  geom_line(alpha = 0.25, aes(group = track)) +
  scale_y_reverse()
```

```{r}
df <- tribble(
~id, ~bp1, ~bp2,
"A", 100, 120,
"B", 140, 115,
"C", 120, 125
)
df
```




```{r}
df |> 
  pivot_longer(
    cols = bp1:bp2,
    names_to = "measurement",
    values_to = "value"
  )
```

