---
title: "R Notebook"
output: html_notebook
---


# 0.0 Imports

```{r}
renv::restore()
```


```{r}
library(tidyverse)
library(palmerpenguins)
library(ggthemes)
```


```{r}
df0 <- data.frame(penguins)
```



```{r}
#1

dim(df0)

```


```{r}
#3

ggplot(
  data=df0,
  mapping=aes(x = flipper_length_mm, y = body_mass_g)
) +
  geom_point(mapping = aes(color = species, shape = species)) +
  geom_smooth(method = "lm") +
  labs(
    title = "Body mass and flipper length",
    subtitle = "Dimensions for Adelie, Chinstrap, and Gentoo Penguins",
    x = "Flipper length (mm)", y = "Body mass (g)", color = "Species", shape = "Species") + 
  scale_color_colorblind()
```


```{r}
# 1) Exercices
dim(df0)

# 2) Scatterplot
ggplot(
  data = df0,
  mapping = aes(y = bill_depth_mm, x = bill_length_mm)
) + 
  geom_point(mapping = aes(color = species, shape=species)) +
  geom_smooth(method='lm') +
  labs(
    title = "Depth vs Length",
    subtitle = "Comparison",
    caption = "Data come from palmerpenguins package"
  ) +
  scale_color_colorblind()

# 3)
ggplot(
  data = df0,
  mapping = aes( x = species, y = bill_depth_mm)
) +
  geom_bar(
    stat="identity", 
    mapping=aes(fill=species)) +
  scale_color_colorblind()

# 5)
  ggplot(data = penguins, mapping = aes(x = bill_depth_mm, y = bill_length_mm)) +
    geom_point()
# I need to mapp the aesthetics
  
# 6) The na.ar argument silences the missings removal.
  ggplot(data = penguins, mapping = aes(x = bill_depth_mm, y = bill_length_mm)) +
    geom_point(na.rm=TRUE)
  
# 7) Added caption to bottom right place
  
# 8)
  ggplot(
    data = penguins,
    mapping = aes(x = flipper_length_mm, y = body_mass_g)
) + 
    geom_point(mapping = aes(colour=bill_depth_mm)) +
    geom_smooth( method="gam", formula = y~s(x) )

# 9) O Geom_smooth é todinho mapeado,mesma cor, no global level
  ggplot(
    data = penguins,
    mapping = aes(x = flipper_length_mm, y = body_mass_g)
  ) + 
    geom_point(mapping = aes(color = island)) +
    geom_smooth(mapping = aes(color = island), se = FALSE )

```

```{r}
ggplot(penguins, aes(x = fct_infreq(species))) +
  geom_bar()
```

```{r}
ggplot(penguins, aes(x = body_mass_g)) +
  geom_histogram(binwidth = 2000)
```

```{r}
ggplot(penguins, aes(x = body_mass_g)) +
  geom_density()

```


Make a bar plot of species of penguins, where you assign
species to the y aesthetic. How is this plot different?

```{r}
ggplot(penguins) +
  geom_bar( mapping = aes( y = species) )

```


How are the following two plots different? Which aesthetic, color or
fill, is more useful for changing the color of bars?
R: Fill is more usefull ok

```{r}
ggplot(penguins, aes(x = species, color = "red")) +
  geom_bar()

ggplot(penguins, aes(x = species, fill = "red")) +
  geom_bar()

```

3. What does the bins argument in geom_histogram()?
Set the number of bins


```{r}
ggplot(penguins, aes(x=bill_length_mm)) +
  geom_histogram(bins = 5)
```


4. Make a histogram of the carat variable in the diamonds dataset that is available when ou load the tidyverse package.Experiment with different binwidth values. What value reveals the most interesint patterns?

R: 0.4 show a decreasing pattern.

```{r}
ggplot(diamonds, aes(x = carat)) +
  geom_histogram( binwidth = .4)
```

```{r}
ggplot(penguins, aes(x = species, y = body_mass_g)) +
  geom_boxplot()
```

```{r}
ggplot(penguins, aes(x = body_mass_g, color = species, fill = species)) +
  geom_density( linewidth = .75, alpha = .5)
```

```{r}
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(position = "fill")
```

```{r}
ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point()
```

```{r}
ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species, shape = species)) +
  facet_wrap(~island)
```

1. The mpg data frame that is bundled with the ggplot2 package contains
234 observations collected by the US Environmental Protection
Agency on 38 car models. Which variables in mpg are categorical?
Which variables are numerical? (Hint: Type ?mpg to read the
documentation for the dataset.) How can you see this information
when you run mpg?
manufacturer, model, trans, drv, fl and class are categorical whereas the remaining are numeric.


```{r}
str(mpg)
```




2. Make a scatterplot of hwy versus displ using the mpg data frame.
Next, map a third, numerical variable to color, then size, then both
color and size, and then shape. How do these aesthetics behave
differently for categorical versus numerical variables?

```{r}
ggplot(mpg, aes(y = hwy, x = displ, color = cyl)) +
  geom_point()
```





3. In the scatterplot of hwy versus displ, what happens if you map a
third variable to linewidth?
R: Error, it is not possible to map linewidth

```{r}
ggplot(mpg, aes(y=hwy, x=displ)) +
  geom_point( linewidth=year )
```




4. What happens if you map the same variable to multiple aesthetics?

```{r}
str(penguins)

ggplot(penguins, aes(y=bill_length_mm, x=bill_depth_mm, color=sex, fill=sex, shape=sex)) +
  geom_point()
```




5. Make a scatterplot of bill_depth_mm versus bill_length_mm
and color the points by species. What does adding coloring by
species reveal about the relationship between these two variables?
What about faceting by species?
R: coloring reveals that they are wuite different regarding bill measures. Faceting give us better vision of that.


```{r}
ggplot(penguins, aes(y = bill_depth_mm, x = bill_length_mm, color = species)) +
  geom_point() +
  facet_wrap(~species)

```



6. Why does the following yield two separate legends? How would you
fix it to combine the two legends?
By removing the labs argument it is possible to combine both legends into one.

```{r}
ggplot(penguins, 
       mapping = aes(
         x = bill_length_mm, y = bill_depth_mm,
         color = species, shape = species
       )) +
  geom_point()
  
```


Create the two following stacked bar plots. Which question can you
answer with the first one? Which question can you answer with the
second one?
R: Throughout the first one I can find out how islands contrates species, whereas the second one shows me how species are spread across islands

```{r}
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(position = 'fill')
ggplot(penguins, aes(x = species, fill = island)) +
  geom_bar(position = 'fill')
ggsave(filename = "pinguizim.png")


```

Run the following lines of code. Which of the two plots is saved as
mpg-plot.png? Why?


```{r}
ggplot(mpg, aes(x = class)) +
  geom_bar()
ggplot(mpg, aes(x = cty, y = hwy)) +
  geom_point()
ggsave("mpg-plot.pdf")

```

```{r}
this_is_a_really_long_name <- 2.5
  
```

```{r}
seq(3,6)
```

```{r}
x <- "Hello
```

