---
title: "R Notebook"
output: html_notebook
---


# 0.0 Imports

```{r}
renv::restore()
```


```{r}
library(tidyverse)
library(nycflights13)
```


# 1.0 Tidy Data

Exercises

1) table 1: represents cases and country population per country and year
   table 2: each observation represents a country, year and specific indicator (cases or population). The three first columns are categorical about the count color
   table 3: each observation represents a rate of TB case per year and country.


2) table 1: I would use mutate
   table 2: I would pivot type and count, them merge
   table 3: I would split the rate column into two strings, using the / as delimitator, then I would name the columns

# 2.0 Lengthening Data

```{r}
billboard_longer <- billboard |> 
  pivot_longer(
    cols = starts_with("wk"),
    names_to = "week",
    values_to = "rank",
    values_drop_na = TRUE
  ) |> 
  mutate(
    week = parse_number(week)
  )
billboard_longer
```


```{r}
billboard_longer |> 
  ggplot(aes(x = week, y = rank)) +
  geom_line(alpha = 0.25, aes(group = track)) +
  scale_y_reverse()
```

```{r}
df <- tribble(
~id, ~bp1, ~bp2,
"A", 100, 120,
"B", 140, 115,
"C", 120, 125
)
df
```



```{r}
df |> 
  pivot_longer(
    cols = bp1:bp2,
    names_to = "measurement",
    values_to = "value"
  )
```


```{r}
# Many variables in column Names
who2 |> pivot_longer(
  cols = !(country:year), # vector of columns that I want to pivot longer
  names_to = c("diagnosis", "gender", "age"), # name of nem created columns
  names_sep = "_", # separator,
  values_to = "count",
  values_drop_na = TRUE # name of the new count column
)
```

```{r}
household
```


```{r}
household |> pivot_longer(
  cols = !family,
  cols_vary = "fastest",
  names_to = c(".value", "child"),
  names_sep = "_",
  values_drop_na = TRUE
)
```
# 3.0 Widening the data

```{r}
cms_patient_experience
```


```{r}
cms_patient_experience |>
  pivot_wider(
    names_from = measure_cd,
    values_from = prf_rate
  ) |> glimpse()
```

```{r}
cms_patient_experience |>
  pivot_wider(
    id_cols = starts_with("org"),
    names_from = measure_cd,
    values_from = prf_rate
  )
```

```{r}
df <- tribble(
~id, ~measurement, ~value,
"A", "bp1", 100,
"B", "bp1", 140,
"B", "bp2", 115,
"A", "bp2", 120,
"A", "bp3", 105
)
df
```

```{r}
df |> pivot_wider(
  id_cols = id,
  names_from = measurement,
  values_from = value
)
```

```{r}
df <- tribble(
~id, ~measurement, ~value,
"A", "bp1", 100,
"A", "bp1", 102,
"A", "bp2", 120,
"B", "bp1", 140,
"B", "bp2", 115
)
df
```


```{r}
df |> 
  pivot_wider(
    names_from = measurement,
    values_from = value
  )
```
```{r}
df |>
  group_by(id, measurement) |> 
  summarize(n = n(), .groups = "drop") |> 
  filter(n > 1)
```

