---
title: "R Notebook"
output: html_notebook
---


# 0.0 Imports



```{r}
library(tidyverse)
library(tidymodels)
library(nycflights13)
tidymodels_prefer()
options(scipen=999)
```

# 1.0 Asimple recipe hor Ames Housing Data

```{r}
set.seed(502)
ames_split <- initial_split(ames, prop = 0.80, strata =
Sale_Price)
ames_train <- training(ames_split)
ames_test <- testing(ames_split)
```


```{r}
simple_ames <-
recipe(Sale_Price ~ Neighborhood + Gr_Liv_Area + Year_Built +
Bldg_Type,
data = ames_train) %>%
step_log(Gr_Liv_Area, base = 10) %>%
step_dummy(all_nominal_predictors())

lm_model <- linear_reg() %>% set_engine("lm")

lm_wflow <-
workflow() %>%
add_model(lm_model) %>%
add_variables(outcome = Sale_Price, predictors = c(Longitude,
Latitude))

lm_wflow <-
lm_wflow %>%
remove_variables() %>%
add_recipe(simple_ames)
lm_wflow

lm_fit <- fit(lm_wflow, ames_train)
#> ══ Workflow
```


```{r}
rf_model <- 
  rand_forest(trees = 1000) |> 
  set_engine("ranger") |> 
  set_mode("regression")

rf_wflow <- 
  workflow() |> 
  add_formula(
  Sale_Price ~ 
  Neighborhood + 
  Gr_Liv_Area + 
  Year_Built + 
  Bldg_Type + 
  Latitude + 
  Longitude) |> 
  add_model(rf_model)

rf_fit <- rf_wflow |> 
  fit(data = ames_train)
```


```{r}
estimate_perf <- function(model, dat) {
# Capture the names of the `model` and `dat` objects
  cl <- match.call()
  obj_name <- as.character(cl$model)
  data_name <- as.character(cl$dat)
  data_name <- gsub("ames_", "", data_name)

reg_metrics <- metric_set(rmse, rsq)

model %>%
  predict(dat) %>%
  bind_cols(dat %>% select(Sale_Price)) %>%
  reg_metrics(Sale_Price, .pred) %>%
  select(-.estimator) %>%
  mutate(object = obj_name, data = data_name)
}
```

```{r}
estimate_perf(lm_fit, ames_train)
```

```{r}
estimate_perf(rf_fit, ames_train)
```

```{r}
estimate_perf(rf_fit, ames_test)
```

```{r}
estimate_perf(lm_fit, ames_test)
```
# 10.1 Resampling methods

## 1.1 Cross-Validation


```{r}
set.seed(1001)
ames_folds <- vfold_cv(ames_train, v = 10)
ames_folds
```

```{r}
ames_folds$splits[[1]] |> analysis() |> dim()
```

## 1.2 Repeated Cross-Validation

```{r}

erro_padrão = desvio_padrao/raizquadrada(N)

vfold_cv(ames_train, v = 10, repeats= 5)
```

## 1.3 Leave-One-Out Cross-Validation


## 1.4 Monte Carlo Cross-Validation


```{r}
mc_cv(ames_train,
      times = 20)
```

## 1.5 Validation Sets


```{r}
set.seed(1002)

val_set <- validation_split(ames_train, prop = 3/4)
val_set
```


```{r}
bootstraps(ames_train, times = 5)
```

## 1.6 Rolling Forecasting Origin Resampling

```{r}
time_slices <- 
  tibble(x = 1:365) |> 
  rolling_origin(initial = 6 * 3,
                 assess = 30,
                 skip = 29,
                 cumulative = FALSE)
head(time_slices)
```

```{r}
data_range <- function(x) {
  summarize(x, 
            first = min(x),
            last = max(x))
}

data_range
```



```{r}

map_dfr(time_slices$splits, ~ analysis(.x) |> data_range())
```
## 1.7 Estimating Performance


```{r}
rf_wflow |> fit_resamples(val_set)
```

```{r}
keep_pred <- control_resamples(
  save_pred = TRUE,
  save_workflow = TRUE)

set.seed(1003)
rf_res <- 
  rf_wflow |> 
  fit_resamples(
    resamples = ames_folds,
    control = keep_pred
  )
rf_res
```

```{r}
collect_metrics(rf_res,
                summarize = FALSE)
```
```{r}
assess_res <- collect_predictions(rf_res)
assess_res
```

```{r}
assess_res |> 
  ggplot(aes(x = Sale_Price, y = .pred)) +
  geom_point(alpha = .15) +
  geom_abline(color = "red") +
  coord_obs_pred() +
  ylab("Predicted")
```

```{r}
over_predicted <- 
  assess_res |> 
  mutate(residual = Sale_Price - .pred) |> 
  arrange(desc(abs(residual))) |> 
  slice(1:2)

ames_train |> 
  slice(over_predicted$.row) |> 
  select(Gr_Liv_Area,
         Neighborhood,
         Year_Built,
         Bedroom_AbvGr,
         Full_Bath)
  
```

```{r}
val_res <- rf_wflow |>
  fit_resamples(resamples = val_set)
val_res
```

```{r}
collect_metrics(val_res)
```


# 10.2 Parallel Processing


Number of Cores
```{r}
parallel::detectCores(logical = FALSE)
```


Number of independent processes that can be simutaneously used:
```{r}
parallel::detectCores(logical = TRUE)
```

# 10.3 Saving the Resampled Objects

```{r}
ames_rec <-
recipe(Sale_Price ~ Neighborhood + Gr_Liv_Area + Year_Built +
Bldg_Type +
Latitude + Longitude, data = ames_train) %>%
step_other(Neighborhood, threshold = 0.01) %>%
step_dummy(all_nominal_predictors()) %>%
step_interact( ~ Gr_Liv_Area:starts_with("Bldg_Type_") ) %>%
step_ns(Latitude, Longitude, deg_free = 20)
lm_wflow <-
workflow() %>%
add_recipe(ames_rec) %>%
add_model(linear_reg() %>% set_engine("lm"))
```

```{r}
lm_fit <- lm_wflow |> 
  fit(data = ames_train)
```

```{r}
extract_recipe(lm_fit, estimated = TRUE)
```

```{r}
get_model <- function(x) {
  extract_fit_parsnip(x) |> tidy()
}

get_model(lm_fit)
```

```{r}
ctrl <-  control_resamples(extract = get_model)

lm_res <- lm_wflow |> 
  fit_resamples(resamples = ames_folds,
                control = ctrl)
lm_res
```

```{r}
lm_res$.extracts[[1]]
```

```{r}
lm_res$.extracts[[1]][[1]]
```

```{r}
all_coef <- map(lm_res$.extracts, ~ .x[[1]][[1]])

all_coef
```

# 10.4 Chapter Summary

```{r}
library(tidymodels)
data(ames)
ames <- mutate(ames, Sale_Price = log10(Sale_Price))
set.seed(502)


ames_split <- initial_split(ames, prop = 0.80, strata =
Sale_Price)
ames_train <- training(ames_split)
ames_test <- testing(ames_split)


ames_rec <-
  recipe(Sale_Price ~ Neighborhood + Gr_Liv_Area + Year_Built +
Bldg_Type +
Latitude + Longitude, data = ames_train) %>%
  step_log(Gr_Liv_Area, base = 10) %>%
  step_other(Neighborhood, threshold = 0.01) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_interact( ~ Gr_Liv_Area:starts_with("Bldg_Type_") ) %>%
  step_ns(Latitude, Longitude, deg_free = 20)

lm_model <- linear_reg() %>% set_engine("lm")

lm_wflow <-
  workflow() %>%
  add_model(lm_model) %>%
  add_recipe(ames_rec)

lm_fit <- fit(lm_wflow, ames_train)

rf_model <-
  rand_forest(trees = 1000) %>%
  set_engine("ranger") %>%
  set_mode("regression")
rf_wflow <-
  workflow() %>%
  add_formula(
  Sale_Price ~ Neighborhood + Gr_Liv_Area + Year_Built +
  Bldg_Type +
  Latitude + Longitude) %>%
  add_model(rf_model)
  set.seed(1001)
ames_folds <- vfold_cv(ames_train, v = 10)
keep_pred <- control_resamples(save_pred = TRUE, save_workflow =
TRUE)

set.seed(1003)

rf_res <- rf_wflow %>% fit_resamples(resamples = ames_folds,
control = keep_pred)

```

# Chapter 11 - Comparing Models with Resampling

## 11.1 Creating Multiple Models with Workflow Sets

```{r}
library(tidymodels)
tidymodels_prefer()
basic_rec <-
  recipe(Sale_Price ~ Neighborhood + Gr_Liv_Area + Year_Built + Bldg_Type +
  Latitude + Longitude, data = ames_train) %>%
  step_log(Gr_Liv_Area, base = 10) %>%
  step_other(Neighborhood, threshold = 0.01) %>%
  step_dummy(all_nominal_predictors())


interaction_rec <-
  basic_rec %>%
  step_interact( ~ Gr_Liv_Area:starts_with("Bldg_Type_") )


spline_rec <-
  interaction_rec %>%
  step_ns(Latitude, Longitude, deg_free = 50)


preproc <-
  list(
  basic = basic_rec,
  interact = interaction_rec,
  splines = spline_rec)

lm_models <- workflow_set(preproc, list(lm = linear_reg()), cross = FALSE)

lm_models

```

```{r}
lm_models <- 
  lm_models |> 
  workflow_map("fit_resamples",
               seed = 123, verbose = TRUE,
               resamples = ames_folds, control = keep_pred)

lm_models
```

```{r}
collect_metrics(lm_models) |> 
  filter(.metric == "rmse")
```


```{r}
four_models <- 
  as_workflow_set(random_forest = rf_res) |> 
  bind_rows(lm_models)
four_models
```
```{r}
library(ggrepel)

autoplot(
  four_models,
  metric = "rsq") +
  geom_text_repel(aes(label = wflow_id),
                      nudge_x = 1/8,
                      nudge_y = 1/100) +
                    theme(legend.position = "none")

```

## 11.2 Comparing Resampled Performance Statistics

```{r}
rsq_indiv_estimates <- 
  collect_metrics(four_models, summarize = FALSE) |> 
  filter(.metric == "rsq")

rsq_wider <- 
  rsq_indiv_estimates |> 
  select(wflow_id, .estimate, id) |> 
  pivot_wider(id_cols = "id", names_from = "wflow_id", values_from = ".estimate")


corrr::correlate(rsq_wider %>% select(-id), quiet = TRUE)
```
## 11.3 Simple Hypothesis Testing Methods

```{r}

```

